### 2015-07-15 Irregular-occ/Irregular-occ.tex
.

@@

>>>>

As explicited in section \ref{Sec: introducao}

@@

\cite{GomesJunior2015} showed from observations made at the Observatório do Pico dos Dias (OPD), Observatoire Haute-Provence (OHP) and European Southern Observatory (ESO) that the orbits of the irregular satellites of the giant planets have systematic errors. The offsets of the observations relative to the JPL ephemeris could be up to 200 mas for some satellites. These differences could be associated with errors in their orbital elements.

We utilize the offsets obtained by \cite{GomesJunior2015} to identify a pattern in the error of the ephemeris. This pattern could be used to extrapolate an offset to the satellite by the time of the occultation predicted. Plots of the offsets over time and true anomaly (see Fig. \ref{} for ??) clearly show that these two parameters are the most important in the differences observed.
